An institutional approach to attention allocation and venture resource mobilization and acquisition

### 2021-03-13 Manuscript.Rmd
Figured out kableextra issue and added more to the manuscript

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
#options(knitr.table.format = "latex")
```

@@

(17)	*Revenue ~  AHC + (AHC | Country)* 
(18)	*Revenue ~  AHC + (AHC x Ease of finding skilled employees | Country)*
(19)	*Revenue ~  AFC + (AFC | Country)*
(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country)*   
(21)	*Revenue ~  AFC + (AFC x VC availability | Country)*   
(22)	*Revenue ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
(23)	*Revenue ~  ASC + (ASC | Country)*   
(24)	*Revenue ~  ASC + (ASC x State of cluster development | Country)*

## Data analysis
I used `r cite_r("r-references.bib")` for all our analyses.
```{r message=FALSE, warning=FALSE, include=FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(ggplot2)
library(psych)
library(knitr)
library(preprocessCore)
library(kableExtra)

@@

#CGI data
```{r message=FALSE, warning=FALSE, include=FALSE}
gci <- import("Data/GCI_2018.xlsx")

@@

#Plotting all countries along the 3 dimensions

```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}

@@

summary_table <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$t$" = "t value"
    , "$p$" = "Pr(>|t|)"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$t$`, `$p$`)}

@@

rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
rownames(hc0_c) <- c("Intercept","Attention to Human capital(AHC)", "HCI", "GC")
#rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
rownames(hc1_c) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees", "HCI", "GC")
#rownames(fc0) <- c("Intercept","Attention to Financial capital")
rownames(fc0_c) <- c("Intercept","Attention to Financial capital", "HCI", "GC")
#rownames(fc1) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs")
rownames(fc1_c) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs", "HCI", "GC")
#rownames(fc2) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability")
rownames(fc2_c) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability", "HCI", "GC")
#rownames(fc3) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps")
rownames(fc3_c) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps", "HCI", "GC")
#rownames(sc0) <- c("Intercept","Attention to Social capital")
rownames(sc0_c) <- c("Intercept","Attention to Social capital", "HCI", "GC")
#rownames(sc1) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")
rownames(sc1_c) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development", "HCI", "GC")

@@

kable(hc_zero, booktabs = T, caption = "Table 1: Effect of attention to human capital", escape = F) %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kable(hc_one, caption = "Table 2: Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_zero, caption = "Table 3: Effect of attention to financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_one, caption = "Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_two, caption = "Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_three, caption = "Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_zero, caption = "Table 7: Effect of attention to social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_one, caption = "Table 8: Effect of congruency of venture attention and institutional level of social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

#kable(sc1_c[,-1], escape = FALSE, caption = "Table 16: Effect of congruency of venture attention and institutional level of social capital - Model with controls")

@@

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#Outcome: Resource acquistion 
library(lme4)

@@

fit11sc <- lmer(equity_sources_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)

@@

#kable(hc00[,-1], escape = FALSE)
#kable(hc11[,-1], escape = FALSE)
#kable(fc00[,-1], escape = FALSE)
#kable(fc11[,-1], escape = FALSE)
#kable(fc22[,-1], escape = FALSE)
#kable(fc33[,-1], escape = FALSE)
#kable(sc00[,-1], escape = FALSE)
#kable(sc11[,-1], escape = FALSE, caption = "This is the table caption")

>>>>

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = F, message = F, fig.pos = "!H", out.extra = "")
#options(knitr.table.format = "latex")
```

@@

(17)	*Revenue ~  AHC + (AHC | Country)* 
(18)	*Revenue ~  AHC + (AHC x Ease of finding skilled employees | Country)*
(19)	*Revenue ~  AFC + (AFC | Country)*
(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country) + (AFC x VC availability | Country) + (AFC x Domestic Credit Gaps | Country)*   
(23)	*Revenue ~  ASC + (ASC | Country)*   
(24)	*Revenue ~  ASC + (ASC x State of cluster development | Country)*

## Data analysis
I used `r cite_r("r-references.bib")` for all our analyses.
```{r message=FALSE, warning=FALSE, include=FALSE}
library(rio)
library(tidyverse)
library(janitor)
library(ggplot2)
library(psych)
library(knitr)
library(preprocessCore)
library(kableExtra)
```

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
#CGI data
gci <- import("Data/GCI_2018.xlsx")

@@

```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
#Plotting all countries along the 3 dimensions

@@

summary_table <- function(x){ x$coefficients %>%
  as.data.frame %>%
    rename(
      "$b$" = "Estimate"
    , "SE" = "Std. Error"
    , "$t$" = "t value"
  ) %>%
  mutate(
    Effect = papaja:::prettify_terms(rownames(.))
  ) %>%
  printnum(
    digits = c(2, 2, 2, 3)
    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
  ) %>%
  select(Effect, `$b$`, `SE`, `$t$`)}

@@

rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
rownames(hc0_c) <- c("Intercept","Attention to Human capital(AHC)", "HCI", "GC")
rownames(hc1_c) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees", "HCI", "GC")
rownames(fc0_c) <- c("Intercept","Attention to Financial capital", "HCI", "GC")
rownames(fc1_c) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs", "HCI", "GC")
rownames(fc2_c) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability", "HCI", "GC")
rownames(fc3_c) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps", "HCI", "GC")
rownames(sc0_c) <- c("Intercept","Attention to Social capital", "HCI", "GC")
rownames(sc1_c) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development", "HCI", "GC")

@@

kable(hc_zero, escape = F, caption = "Effect of attention to human capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kable(hc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_zero, escape = F, caption = "Effect of attention to financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(fc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_two, escape = F, caption = "Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(fc_three, escape = F, caption = "Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

kbl(sc_zero, escape = F, caption = "Effect of attention to social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")

kbl(sc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of social capital") %>%
  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Outcome: Resource acquistion 
library(lme4)

@@

fit11sc <- lmer(equity_sources_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)
```

```{r echo=FALSE}
#summary tables

@@

hc <- cbindX(hc11[,-1], hc00[,-1]) 
fc <- cbindX(fc11[,-1], fc00[,-1]) 
sc <- cbindX(sc11[,-1], sc00[,-1])

```{r echo=FALSE}
#Print summaries

kable(hc, escape = F, caption = "Effect on total employees") %>%
  add_header_above(c(" ", "Congruence" = 3, "AHC only" = 3), italic = T)

kable(fc, escape = F, caption = "Effect on capital raised") %>%
  add_header_above(c(" ", "Congruence" = 3, "AFC only" = 3), italic = T)

kable(fc22[,-1], escape = F, caption = "Effect on capital raised")

kable(fc33[,-1], escape = F, caption = "Effect on capital raised")

kable(sc, escape = F, caption = "Effect on sources of capital") %>%
  add_header_above(c(" ", "Congruence" = 3, "ASC only" = 3), italic =T)

```{r}
#Outcome: Revenue
library(lme4)

fit0_hc <- lmer(revenue_tot ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

fit1_hc <- lmer(revenue_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

fit0_fc <- lmer(revenue_tot ~ + accel_ben_rank_direct_funding+ (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

fit1_fc <- lmer(revenue_tot ~ + accel_ben_rank_direct_funding*EOSQ425+ accel_ben_rank_direct_funding*EOSQ089 + accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

fit0_sc <- lmer(revenue_tot ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)

fit1_sc <- lmer(revenue_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)

```{r}
#summary tables

hc_0 <- summary_table(summary(fit0_hc))
hc_1 <- summary_table(summary(fit1_hc))
fc_0 <- summary_table(summary(fit0_fc))
fc_1 <- summary_table(summary(fit1_fc))
sc_0 <- summary_table(summary(fit0_sc))
sc_1 <- summary_table(summary(fit1_sc))

rownames(hc_0) <- c("Intercept","Attention to Human capital")
rownames(hc_1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
rownames(fc_0) <- c("Intercept","Attention to Financial capital")
rownames(fc_1) <- c("Intercept","AFC", "Financing of SMEs", "VC Availability", "Domestic Credit Gaps", "AFCxFinancing of SMEs", "AFCxVC Availability", "AFCxDomestic Credit Gaps")
rownames(sc_0) <- c("Intercept","Attention to Social capital")
rownames(sc_1) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")

hc_r <- cbindX(hc_1[,-1], hc_0[,-1]) 
fc_r <- cbindX(fc_1[,-1], fc_0[,-1]) 
sc_r <- cbindX(sc_1[,-1], sc_0[,-1])

```{r}
#Print summaries

kable(hc_r, escape = F, caption = "Effect on revenues", digits = 0) %>%
  add_header_above(c(" ", "Congruence" = 3, "AHC only" = 3), italic = T) %>%
kable_styling(font_size = 8)

kable(fc_r, escape = F, caption = "Effect on revenues", digits = 0) %>%
  add_header_above(c(" ", "Congruence" = 3, "AFC only" = 3), italic = T) %>%
kable_styling(font_size = 8)

kable(sc_r, escape = F, caption = "Effect on revenues", digits = 0) %>%
  add_header_above(c(" ", "Congruence" = 3, "ASC only" = 3), italic =T) %>%
kable_styling(font_size = 8)
